---
title: 'Mushroom and Stomach Cancer: Meta-analysis'
output:
  html_document:
    df_print: paged
---


# LOAD REQUIRED PACKAGES AND FUNCTIONS -----------------------------------------
```{r, message=FALSE}
library(olsrr) # linear regression
library(tidyverse) # general stuff
library(hrbrthemes) # pretty plots
library(ggplot2) # pretty plots
library(plotly) # interactive plots
library(gapminder) # interactive plots
library(pastecs) # stat.desc
library(metafor) # for meta-analysis: mixed-effects logistic and Poisson regression models
library(meta) # meta-regression, GLMM, forest plots,(subgroup) meta-analyses.
library(sp) # spatial data
library(rgdal) #  projection/transformation operations for shapefiles
library(sf) # Simple Features for R
library(rnaturalearth)
library(tmap) # cool maps
library(ggpubr) # 'ggplot2' Based Publication Ready Plots
library(ggpmisc) #Miscellaneous Extensions to 'ggplot2'
library(spData)
library(cowplot)# plot grid
library(ggsci)
library(RColorBrewer)
library(ggrepel)
library(readxl)
```

# Objectives:
## Determine the association between mushroom consumption and stomach cancer
## Characterize the modifiers for the mushroom-stomach cancer
## Factors to explore: WHO region, Study design, Smoking and H.pylori rates, Income group, Mean age, proportion male


# read data -----------------------------------------
```{r}
rm(list=ls())
#dat1=read.csv("Main.csv")
#dat=read.csv("data/stop3.csv")
#dat<- read_excel("data/HPV.xlsx")
#dat=read.csv("data/pool2.csv")
dat=read.csv("data/HPV.csv")

```


# Meta-analysis using Maximum likehood Adjusted-----------------------------------------
```{r}

l1=is.na(dat$RR)
dat=dat[!l1,]

dat$TE=log(dat$RR)
dat$lower <- log(dat$RR_L)
dat$upper <- log(dat$RR_U)
dat$seTE <- (dat$upper - dat$lower)/3.92



#l1=is.na(dat$CRR)
#dat=dat[!l1,]


#dat$TE=log(dat$CRR)
#dat$seTE=(log(dat$CRR_U-log(dat$CRR_L))/(3.92))



m <- metagen(TE,
             seTE,
             data=dat,
             #studlab=paste(Study,Age,Male, Country,sep = ","),
             studlab=paste(Author,Year_Publication,Country,sep = ", " ),
             comb.fixed = T,
             comb.random = T,
             hakn = F,
             prediction=F,
             sm="RR")

m

```


# Meta-analysis using Maximum likehood UnAdjusted-----------------------------------------
```{r, eval=T}

dat=read.csv("data/HPV.csv")

l1=is.na(dat$RR_Crude)
dat1=dat[!l1,]

dat1$TE=log(dat1$RR_Crude)
dat1$lower <- log(dat1$RR_Crude_L)

dat1$upper <- log(dat1$RR_Crude_U)

dat1$seTE <- (dat1$upper - dat1$lower)/3.92

mm <- metagen(TE,
             seTE,
             data=dat1,
             #studlab=paste(Study,Age,Male, Country,sep = ","),
             studlab=paste(Author,Year_Publication,Country,sep = ", " ),
             comb.fixed = T,
             comb.random = T,
             hakn = F,
             prediction=F,
             sm="RR")

mm

```






#Influence analysis  using leave-one-out -----------------------------------------
```{r}
pdf("figs/InfluencialPlots.pdf", width = 10, height = 20)
forest(metainf(m, pooled = "random"))
dev.off()

inf1=metainf(m, pooled = "random")
summary(inf1)
```


```{r fig.height=3, fig.width=4, echo=FALSE,warning=FALSE}
forest(inf1,
       leftlabs = c("Study"),
       digits = 2,
       col.by="black",
       #sortvar = "TE",
       squaresize=0.5,
       col.square="blue",
       col.diamond="maroon",
       col.diamond.lines="maroon",
       xlab="risk ratio for HPV vaccination and cervical cancer screening",
       print.pval.Q = T,
       digits.pval.Q=4,
       print.tau2=F,
       #xlim = c(0, 1.6), at = c(0,0.5,1.6),
       backtransf = T)

```



# trim and fill : Risk ratio -----------------------------------------



```{r}
tf2 <- trimfill(m)
summary(tf2)
pdf("figs/Trimmed.pdf", width = 10, height = 10)
funnel(tf2)
dev.off()
funnel(tf2, pch = ifelse(tf2$trimfill, 1, 16),
       level = 0.9, comb.random = T,backtransf = T)
#
```




# Funnel plots : Risk ratio -----------------------------------------
```{r}

pdf("figs/FunnelPlotFinal.pdf", width = 10, height = 10)
funnel(m,xlab = "log transformed proportions",studlab = F)
dev.off()

metabias(m, method="linreg")# Egger's linear regression test

```


```{r}

metabias(m, method="rank")

```



# Plot figure 1: Overall: Adjusted
```{r,fig.height=3, fig.width=4, echo=FALSE,warning=FALSE}


pdf("figs/Overall_Adjusted.pdf", width = 10, height = 5)
forest(m,sortvar = TE,test.overall = T, overall= T, overall.hetstat = T,
       colgap.forest.left = "0.38 cm",print.byvar = F,
       squaresize=0.5, col.square="navy",
       col.diamond="maroon", col.diamond.lines="maroon",
       col.by="black",leftcols=("studlab"),leftlabs = c("Study, Year, Country"),
       rightlabs = c("RR","95% CI","Weight"), just = "center", just.addcols = "center",
       print.zval = FALSE,text.fixed="Overall (Fixed-Effect Model)",text.random="Overall (Random-Effect Model)",comb.random = T,comb.fixed = F, print.pval.Q = T,
       digits.pval.Q=4,
       print.tau2=F,
       test.overall.fixed=FALSE,test.overall.random = F)
dev.off()
#0.75  (0.61-0.92)
```


# Plot figure 1: Overall: unadjusted
```{r,fig.height=3, fig.width=4, echo=FALSE,warning=FALSE}


pdf("figs/Overall_Crude.pdf", width = 10, height = 4)
forest(mm,sortvar = TE,test.overall = T, overall= T, overall.hetstat = T,
       colgap.forest.left = "0.38 cm",print.byvar = F,
       squaresize=0.5, col.square="navy",
       col.diamond="maroon", col.diamond.lines="maroon",
       col.by="black",leftcols=("studlab"),leftlabs = c("Study, Year, Country"),
       rightlabs = c("RR","95% CI","Weight"), just = "center", just.addcols = "center",
       print.zval = FALSE,text.fixed="Overall (Fixed-Effect Model)",text.random="Overall (Random-Effect Model)",comb.random = T,comb.fixed = F, print.pval.Q = T,
       digits.pval.Q=4,
       print.tau2=F,
       test.overall.fixed=FALSE,test.overall.random = F)
dev.off()
#0.75  (0.61-0.92)
```



#  Begg's rank test
```{r}

metabias(m, method="rank")

```

```{r}
dat7=read.csv("data/HPV.csv")
library(reshape)

l1=reshape(dat7, varying=list(RR= c("RR_1dose", "RR_2dose", "RR_3dose"),
                            LCI= c("RR_L_1dose", "RR_L_2dose","RR_L_3dose"),
                            UCI= c("RR_U_1dose", "RR_U_2dose","RR_U_3dose")), 
          v.names=c("RR", "LCI", "UCI"), 
          # that was needed after changed 'varying' arg to a list to allow 'times' 
          direction="long",  
          times=1:3,        # substitutes number for T1 and T2
          timevar="times")  # to name the time col

l1$times=factor(l1$times)

levels(l1$times)=c("First Dose", "Second Dose", "Third Dose")



l2=is.na(l1$RR)
dat2=l1[!l2,]

dat2$TE=log(dat2$RR)
dat2$seTE=(log(dat2$UCI-log(dat2$LCI))/(3.92))



mmm <- metagen(TE,
             seTE,
             data=dat2,
             studlab=paste(Author,Year_Publication,Country,sep = ", " ),
             comb.fixed = F,
             comb.random = T,
             prediction=F,
             sm="RR")

mmm

m2<-update.meta(mmm, 
                byvar=dat2$times, 
                comb.random = TRUE, 
                comb.fixed = FALSE)
m2
```

# Plot figure 3: Dose response
```{r,fig.height=3, fig.width=4, echo=FALSE,warning=FALSE}


pdf("figs/Dose.pdf", width = 10, height = 8)
forest(m2,sortvar = TE,test.overall = F, overall= F, overall.hetstat = T,
       colgap.forest.left = "0.38 cm",print.byvar = F,
       squaresize=0.5, col.square="navy",
       col.diamond="maroon", col.diamond.lines="maroon",
       col.by="black",leftcols=("studlab"),leftlabs = c("Study, Year, Country"),
       rightlabs = c("RR","95% CI","Weight"), just = "center", just.addcols = "center",
       print.zval = FALSE,text.fixed="Overall (Fixed-Effect Model)",text.random="Dose- specific random-effect estimates",comb.random = T,comb.fixed = F, print.pval.Q = T,
       digits.pval.Q=4,
       print.tau2=F,
       test.overall.fixed=FALSE,test.overall.random = F)
dev.off()
#0.75  (0.61-0.92)
```





# Plot figure 4: Regions
```{r,fig.height=3, fig.width=4, echo=FALSE,warning=FALSE}
who<- update(m, byvar=WHO,print.byvar=F)

pdf("figs/WHO.pdf", width = 10, height = 8)
forest(who,sortvar = TE,test.overall = T, overall= T, overall.hetstat = T,
       colgap.forest.left = "0.38 cm",print.byvar = F,
       squaresize=0.5, col.square="navy",
       col.diamond="maroon", col.diamond.lines="maroon",
       col.by="black",leftcols=("studlab"),leftlabs = c("Study, Year, Country"),
       rightlabs = c("RR","95% CI","Weight"), just = "center", just.addcols = "center",
       print.zval = FALSE,text.fixed="Overall (Fixed-Effect Model)",text.random="Overall (Random-Effect Model)",comb.random = T,comb.fixed = F, print.pval.Q = T,
       digits.pval.Q=4,
       print.tau2=F,
       test.overall.fixed=FALSE,test.overall.random = F)
dev.off()
#0.75  (0.61-0.92)
```
# Plot figure 4: Study design
```{r,fig.height=3, fig.width=4, echo=FALSE,warning=FALSE}
design<- update(m, byvar=Study_Design.1,print.byvar=F)

pdf("figs/Design.pdf", width = 10, height = 8)
forest(design,sortvar = TE,test.overall = T, overall= T, overall.hetstat = T,
       colgap.forest.left = "0.38 cm",print.byvar = F,
       squaresize=0.5, col.square="navy",
       col.diamond="maroon", col.diamond.lines="maroon",
       col.by="black",leftcols=("studlab"),leftlabs = c("Study, Year, Country"),
       rightlabs = c("RR","95% CI","Weight"), just = "center", just.addcols = "center",
       print.zval = FALSE,text.fixed="Overall (Fixed-Effect Model)",text.random="Overall (Random-Effect Model)",comb.random = T,comb.fixed = F, print.pval.Q = T,
       digits.pval.Q=4,
       print.tau2=F,
       test.overall.fixed=FALSE,test.overall.random = F)
dev.off()
#0.75  (0.61-0.92)
```


# Plot figure 4: score
```{r,fig.height=3, fig.width=4, echo=FALSE,warning=FALSE}
score<- update(m, byvar=Score,print.byvar=F)

pdf("figs/Score.pdf", width = 10, height = 8)
forest(score,sortvar = TE,test.overall = T, overall= T, overall.hetstat = T,
       colgap.forest.left = "0.38 cm",print.byvar = F,
       squaresize=0.5, col.square="navy",
       col.diamond="maroon", col.diamond.lines="maroon",
       col.by="black",leftcols=("studlab"),leftlabs = c("Study, Year, Country"),
       rightlabs = c("RR","95% CI","Weight"), just = "center", just.addcols = "center",
       print.zval = FALSE,text.fixed="Overall (Fixed-Effect Model)",text.random="Overall (Random-Effect Model)",comb.random = T,comb.fixed = F, print.pval.Q = T,
       digits.pval.Q=4,
       print.tau2=F,
       test.overall.fixed=FALSE,test.overall.random = F)
dev.off()
#0.75  (0.61-0.92)
```





```{r male}
output.metareg=metareg(m,Time)
meta::bubble(output.metareg,
       xlab = "study year",
       col.line = "blue",
       studlab = TRUE)

```





